---
title: "DAVe.docs"
bibliography: references.bib
link-citations: true
site: bookdown::bookdown_site
---

<meta charset="utf-8" />

```{r,echo=FALSE, warning=FALSE,message=FALSE}
library(dave.help)
```

# Getting Started {#getting_started}
```{r, child=c('partial/001-getting_started.Rmd')}
```

## Quickstart {#quickstart}
```{r, child=c('partial/002-quickstart.Rmd')}
```

## Workflows {#workflows}
```{r, child=c('partial/003-workflows.Rmd')}
```

# Modules {#modules}

## Data {#data}
### Summary
```{r, child=c('partial/004-data.Rmd')}
```

### Reference
```{r, child=c('partial/api/data.Rmd')}
```


## Preprocessing {#preproc}
### Summary
```{r, child=c('partial/preproc.Rmd')}
```

### Reference
```{r, child=c('partial/api/preproc.Rmd')}
```

## Statistics {#stats}
### Reference
```{r, child=c('partial/api/stats.Rmd')}
```

## Clustering {#cluster}
### Reference
```{r, child=c('partial/api/cluster.Rmd')}
```

## Multivariate Analysis{#multivariate}
### Reference
```{r, child=c('partial/api/multivariate.Rmd')}
```


## Pathway Analysis {#pathway}
### Reference
```{r, child=c('partial/api/pathway.Rmd')}
```

## Predictive Modeling {#model}
### Reference
```{r, child=c('partial/api/model.Rmd')}
```


## Network Analysis {#network}
### Summary
```{r, child=c('partial/network_quickstart.Rmd')}
```

### Publication quality networks
```{r, child=c('partial/dave_network_to_cytoscape.Rmd')}
```

### Reference
```{r, child=c('partial/api/network.Rmd')}
```

